---
title: "Coding Exercises"
output: html_notebook
---
```{r}
source("New_R_Setup.R")
```

```{r}
data("knz_bison")
```

Create a new column in the bison dataset that calculates the individual’s age at the time of observation.
```{r}
knz_bison <- knz_bison %>%
    mutate(age = rec_year - animal_yob)
```

  
Write a function that will first filter the bison dataset based on any user-specified weight threshold (returning the filtered dataset).
```{r}
filter_bison <- knz_bison %>%
  filter(animal_weight>400)%>%
    return(filter_bison)

```

  
Create a boxplot showing weight distribution between male and female bison, and then conduct a t-test to see if weight is significantly difference between males and females.
```{r}
filter_bison %>%
  ggplot(aes(x = animal_sex, y = animal_weight, fill = animal_sex)) +
  geom_boxplot() +
  labs(
    title = "Bison Weight Distribution by Sex",
    x = "Sex",
    y = "Weight (kg)"
  ) +
  theme_minimal()
```

```{r}
t_test_result <- t.test(animal_weight ~ animal_sex, data = filter_bison)
t_test_result

```
  
The t-test indicates a statistically significant difference in mean weight between male and female bison (t = -4.56, p < 0.001), with males (mean = 905.4 kg) being, on average, about 40 kg heavier than females (mean = 865.7 kg).